### 2021-07-21 doc/thesis/chapters/hls.tex
comment dividers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{High-Level Synthesis}
\label{cha:HLS}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{State Of The Art}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Functionality}
transform high-level code to HDL

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Language Support}

%%%%%%%%%%%%%%%%%%%%
\subsection{\cplusplus}

%%%%%%%%%%%%%%%%%%%%
\subsection{SystemC}

\section{Coding}

%%%%%%%%%%%%%%%%%%%%
\subsection{Compiler Directives (\#pragma's)}

%%%%%%%%%%%%%%%%%%%%
\subsection{Data types}

%%%%%%%%%%%%%%%%%%%%
\subsection{Functions}

%%%%%%%%%%%%%%%%%%%%
\subsection{Loops}

%%%%%%%%%%%%%%%%%%%%
\subsection{Conditional statements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Testbench}

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{C Simulation}

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{C/RTL Co-Simulation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Advantages / Disadvantages}
easy and much faster to get complex HDL code, such as image/video processing, through libraries like OpenCV. However, it is less optimized, and a developer still needs to have a strong hardware background, to be able to understand what is being generated in hardware from x lines of code in HLS/Cpp.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{High-Level Synthesis}
\label{cha:HLS}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{State Of The Art}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Functionality}
transform high-level code to HDL

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Language Support}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\cplusplus}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SystemC}

In the latest Xilinx HLS tools 'Vitis HLS' and 'Vivado HLS', the language SystemC is already deprecated \cite{VivadoHlsSystemC}.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coding}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Compiler Directives (\#pragma's)}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Data types}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Functions}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Loops}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Conditional statements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Testbench}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{C Simulation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{C/RTL Co-Simulation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Advantages / Disadvantages}

easy and much faster to get complex HDL code, such as image/video processing, through libraries like OpenCV. However, it is less optimized, and a developer still needs to have a strong hardware background, to be able to understand what is being generated in hardware from x lines of code in HLS/Cpp.
